The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-05-23 ms/ms.tex
overleaf

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/violins.png}
\caption{Global annual gross primary production (GPP) and net ecosystem production (NEP) across the PPE within each of our six forcing scenarios. Markers are drawn for 10 and 0.28 PgC bins for GPP and NEP, respectively. The marker area is proportional to the number of simulations falling in that bin. In each case the ellipse is centered about the default simulation.}
\label{fig:violins}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/variance.pdf}
\caption{needs caption}
\label{fig:variance}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/ranges.png}
\caption{Global annual gross primary production (GPP) and net ecosystem production (NEP) across six forcing scenarios. Circles mark the CLM5.1 default simulation, and the bars span the ensemble ranges.}
\label{fig:ranges}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/variance.pdf}
\caption{Cumulative fraction of variance explained by the most influential parameters on gross primary production and canopy evaporation. For example approximately 96\% of canopy evaporation variance is explained by the first ten parameters regardless of forcing, whereas between 74 and 92\% of GPP variance is explained by the first ten parameters. Only the top 50 parameters are shown (of 193) to improve the visualization. Note that parameter rankings differ by variable.}
\label{fig:variance}
\end{figure}
